Manuscript

### 2014-09-05 inst/simulation/manuscript.Rmd
...

```{r figure-3-init-2000}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study)
populationSizes2000 <- validation$getValidationTemporalPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
validation$summarizePopulationSize(populationSizes2000)

>>>>

```{r figure-3-init-2000}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study, populationSizeOverEstimate=20000)
populationSizes2000 <- validation$getValidationTemporalPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
validation$summarizePopulationSize(populationSizes2000)
